HGP analysis: fit model

### 2019-03-26 rick/final/3_fit_model_compareModels.Rmd
update

#plinkPath <- args[2] 
plinkPath <- '/Users/luke/Documents/QualityPaper/ProcessedData' #'/Users/luke/genomes/genomes/hg19/plink/'

#chr <- args[3]
plinkName <- 'PublishedVariants'

@@

message("plink data loaded")
```
get rsIDs and add them as rownames for genotype data
```{r}
data_bim <- fread(paste0(plinkPath,'chr',chr,'.bim'), 
                  col.names = c('Chr','rsID','X',
                                'Pos','Ref','Alt'))

@@

```{r}
fam_file <-fread(paste0(plinkPath,'chr',chr,'.fam'), 
                  col.names=c('sample','a','b','c','d','e'))

@@

saveRDS(data_fit, 
	file.path("./data/preprocessed/subsets",
	paste0("fits_chrom_", chr, "_LFA.rds")))

write.table(data_fit[-2], 
              file.path("./data/preprocessed/subsets", 
                        paste0("fits_chrom_", chr, "_LFA.txt")),
              quote = FALSE,
              row.names = FALSE)
rm(data_fit)
```
#PCA
```{r, warning=FALSE}
#load PCA
library(data.table)
samples = fread('/Users/luke/Documents/PCAperPop/Name_Pop_Qual_PC1_PC2_PC3_PC4_PC5.txt')
PC <- as.matrix(samples[,c('PC1','PC2','PC3','PC4','PC5')])
PC <- cbind(PC, 1)

@@

saveRDS(data_fit_PCA, 
	file.path("./data/preprocessed/subsets",
	paste0("fits_chrom_", chr, "_PCA.rds")))

write.table(data_fit_PCA[-2], 
              file.path("./data/preprocessed/subsets", 
                        paste0("fits_chrom_", chr, "_PCA.txt")),
              quote = FALSE,
              row.names = FALSE)
rm(data_fit_PCA)
```
#Population
```{r, warning=FALSE}

@@

tic("fitting model")
labels <- rownames(data_genotype)
data_fit_Pop <- 
	data_genotype %>%
	as_tibble() %>%
	transmute(
	fit = future_pmap(., fit_glm,
	LF= testModel, 
	trait=avg_qual_mean),
		rsID=labels)  %>%
	unnest(fit) %>%
	mutate(l= rep(c("data","stat"), n()/2))%>%
	spread(l, fit)%>%
	unnest(stat)
   toc()

saveRDS(data_fit_Pop, 
	file.path("./data/preprocessed/subsets",
	paste0("fits_chrom_", chr, "_Pop.rds")))

write.table(data_fit_Pop[-2], 
              file.path("./data/preprocessed/subsets", 
                        paste0("fits_chrom_", chr, "_Pop.txt")),
              quote = FALSE,
              row.names = FALSE)

rm(data_fit_Pop)
```

>>>>

#plinkPath <- args[2] 
plinkPath <- '/Users/luke/Documents/QualityPaper/ProcessedData/' #'/Users/luke/genomes/genomes/hg19/plink/'
DataPath <- '~/Documents/QualityPaper/ProcessedData/'
#chr <- args[3]
plinkName <- 'Significant_Positions'

@@

message("plink data loaded")
```
get rsIDs and add them as rownames for genotype data
```{r}
data_bim <- fread(paste0(plinkPath,plinkName,'.bim'), 
                  col.names = c('Chr','rsID','X',
                                'Pos','Ref','Alt'))

@@

```{r}
fam_file <-fread(paste0(plinkPath,plinkName,'.fam'), 
                  col.names=c('sample','a','b','c','d','e'))

@@

saveRDS(data_fit, 
	file.path(DataPath,
	paste0("fits_",plinkName, "_LFA.rds")))

write.table(data_fit[-2], 
              file.path(DataPath, 
                        paste0("fits_",plinkName,"_LFA.txt")),
              quote = FALSE,
              row.names = FALSE)
rm(data_fit)
```
#PCA
```{r, warning=FALSE}
#load PCA
library(data.table)
samples = fread('/Users/luke/Documents/PCAperPop/Name_Pop_Qual_PC1_PC2_PC3_PC4_PC5.txt')
PC <- as.matrix(samples[,c('PC1','PC2','PC3','PC4','PC5')])
PC <- cbind(PC, 1)

@@

saveRDS(data_fit_PCA, 
	file.path(DataPath,
	paste0("fits_",plinkName, "_PCA.rds")))

write.table(data_fit_PCA[-2], 
              file.path(DataPath, 
                        paste0("fits_",plinkName, "_PCA.txt")),
              quote = FALSE,
              row.names = FALSE)
rm(data_fit_PCA)
```
#Population
```{r, warning=FALSE}

@@

#split data to run separately
chunks <- split(as.data.frame(data_genotype), (as.numeric(1:nrow(data_genotype)) - 1) %/% 5000) 
i<-1
out = list()
for(chunk in chunks){
	print(i)

tic("fitting model")
labels <- rownames(chunk)
out <- 
	chunk %>%
	as_tibble() %>%
	transmute(
	          fit = future_pmap(., fit_glm,
	          LF = testModel, 
	          trait = avg_qual_mean),
		        rsID = labels)  %>%
	unnest(fit)%>%
	mutate(l= rep(c("data","stat"), n()/2))%>%
	spread(l, fit)%>%
	unnest(stat)
   toc()

   if(i==1){
   write.table(unlist(out), 
              file.path(DataPath, 
                        paste0("fits_",plinkName, "_Pop.txt")),
              quote = FALSE,
              row.names = FALSE)}
      if(i!=1){
   write.table(unlist(out), 
               append = TRUE,
               file.path(DataPath, 
                        paste0("fits_",plinkName, "_Pop.txt")),
              quote = FALSE,
              row.names = FALSE,
              col.names = FALSE)}

i <- i+1
}

```
